Additional analysis

### 2018-07-15 03_additional-analysis.Rmd
Add additional analysis to supplement

m_amount_cif_full <-update(m_amount_cif, . ~ . + 
                             favor_humanitarian_bin +
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)
```

@@

ggplot(coefs_posterior, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())
```

@@

ggplot(coefs_posterior_likely, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary_likely, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())
```

>>>>

m_amount_cif_full <- update(m_amount_cif, . ~ . + 
                             favor_humanitarian_bin +
                             give_charity_3 + volunteer + political_knowledge_bin +
                             ideology_bin + education_bin + religiosity_bin +
                             income_bin + age_bin)
```

@@

amount_coefs_full <- ggplot(coefs_posterior, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())

amount_coefs_full %T>%
  print() %T>% 
  ggsave(., filename = here("output", "figures", "amount-coefs-full.pdf"),
         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "amount-coefs-full.png"),
         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
```

@@

likely_coefs_full <- ggplot(coefs_posterior_likely, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary_likely, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())

likely_coefs_full %T>%
  print() %T>% 
  ggsave(., filename = here("output", "figures", "likely-coefs-full.pdf"),
         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = here("output", "figures", "likely-coefs-full.png"),
         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
```
